---
title: "Bank Full Analysis"
author: "Vijay S"
date: "27 February 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)
library(utils)
library(corrplot)
bankf <- read.csv("bank-full.csv",sep = ';')
View(bankf)
```

# Bivariate Analysis
## - Crosstab Analysis  
### - To identofy the relation between two catagorical columns

```{r}
table(bankf$job,bankf$education)
```

```{r}
job_edu <- as.data.frame(table(bankf$job,bankf$education))
head(job_edu)
names(job_edu) = c("Job","Education","Frequency")
```
```{r}
ggplot(job_edu,aes(x=Education,y=Job)) + geom_point()
```

```{r}
ggplot(job_edu,aes(x=Education,y=Job,size=Frequency,color=Frequency)) + geom_point()
```

```{r}
table(bankf$job,bankf$marital)
job_mar <- as.data.frame(table(bankf$job,bankf$marital))
View(job_mar)
names(job_mar) = c("Job","Marital","Frequency")
ggplot(job_mar,aes(x=Job,y=Marital,size=Frequency,color=Frequency)) + geom_point() + coord_flip()
```

```{r}
job_mar1=as.data.frame(table(bankf$job,cut(bankf$balance,breaks = 5,
                                           labels = c("Group 1","Group 2","Group 3","Group 4","Group 5"))))
names(job_mar1) = c("Job","Balance_Group","Frequency")
View(job_mar1)
ggplot(job_mar1,aes(x=Balance_Group,y=Job,size=Frequency,color=Frequency)) + geom_point()
```
```{r}
ggplot(job_mar1,aes(x=Balance_Group,y=Job,fill=-Frequency)) + geom_tile()
```

## Chi Square Test
### H0 -> groups are independent
### H1 -> they are dependent
```{r}
chisq.test(bankf$job,bankf$education)
```
## Step - 1
### To find factor columns in a dataset
```{r}
get_factor <- function(x){
  v=c()
  for (i in 1:ncol(x)) {
   if(is.factor(x[,i]))
    v = append(v,names(x)[i])
  }
  return(v)
}
get_factor(bankf)   

# To find factor columns in a dataset
get_factors = function(df){
  v = sapply(df,is.factor)
  return(names(df)[v])
}
get_factors(bankf)
```
## Step - 2
### To find all the combination of factor columns
```{r}
factors_comb=combn(get_factors(bankf),2,simplify = F)
factors_comb
factors_comb[[1]][1]
```
## Step - 3
### Loop through each combination
```{r}
for (comb in factors_comb) {
  #print(combn)
  chi_res = chisq.test(bankf[,comb[1]], bankf[,comb[2]])
  #print(c(comb[1],comb[2],chi_res$p.value))
  if(chi_res$p.value < 0.05){
    print(comb)
  }
}

for (comb in factors_comb) {
  chi_res = chisq.test(bankf[,comb[1]], bankf[,comb[2]])
  print(c(comb[1],comb[2],chi_res$p.value))
}
```
## Automate Correlation Analysis
#### Step - 1 Identify numerical column
#### Step - 2 Get combinations
#### Step - 3 For each combinations get correlation value
#### Step - 4 Filter only those combination whose abs value is > 0.75
#### Step - 5 Sort the result based on abs value

###### Function to calculate correlation analysis
```{r}
Corr_Analysis <- function(x){
  a=sapply(x, is.numeric)
  x=na.omit(x)
  numeric_comb <- combn(names(x)[a],2,simplify = F)
  i=1
  v1=c()
  for (comb in numeric_comb) {
    corr_anal = cor(x[,comb[1]], x[,comb[2]])
    
    if(abs(corr_anal) > 0.075){
      v1$num1[i] = as.character(comb[1])
      v1$num2[i] = as.character(comb[2])
      v1$abs.value[i] = abs(corr_anal)
      i=i+1
    }
  }
  v1=data.frame(v1,stringsAsFactors = F)
  return(v1 %>% arrange(-abs.value))
}
Corr_Analysis(bankf)

```
```{r}
modi = read.csv("narendramodi_tweets.csv")
View(bankf)
```
```{r}
q1 = quantile(bankf$duration, 0.25, na.rm = T)
q2 = quantile(bankf$duration, 0.5, na.rm = T)
q3 = quantile(bankf$duration, 0.75, na.rm = T)
val_2per = quantile(bankf$duration,0.02,na.rm = T)
val_98per = quantile(bankf$duration,0.98,na.rm = T)
print(c(q1, q2, q3))
iqr = q3-q1
iqr
lw = q1 - 1.5 * iqr
uw = q3 + 1.5 * iqr
print(c(lw,uw,val_2per,val_98per))

outlier = bankf %>% filter((duration<lw) | (duration>uw)) %>% arrange(-duration)
outlier
nrow(outlier) / sum(!is.na(bankf$duration))*100

```

```{r}
bankf %>% group_by(bankf$y)
```

